The zero--one laws of Kolmogorov and Hewitt--Savage in categorical probability

### 2019-12-03 categorical-zero-one.tex
Push argument for causality of Kl(H)

    It follows that $\prod_i X_i$ is an infinite tensor product in $\Kl(H)$; the preservation condition is easily verified since adding another factor to this product again gives the infinite product. The Kolmogorov product condition is similarly immediate to verify.
\end{proof}

>>>>

    It follows that $\prod_i X_i$ is an infinite tensor product in $\Kl(H)$; the preservation condition is easily verified since adding another factor to this product again gives the infinite product. The Kolmogorov product condition is similarly immediate to verify.
\end{proof}
\begin{proposition}
    $\Kl(H)$ is causal.
\end{proposition}
\begin{proof}
    We are given spaces $A, X, Y, Z$, and continuous maps $f:A \to HX, g: X \to HY, h_1,h_2: Y \to HZ$.
    We assume that two maps $X \to H(W \times Z)$ are equal.
    They are given by
    \[a \mapsto \cl\left(\bigcup_{x \in f(a), y \in g(x)} h_1(y) \times \{y\}\right),\ x \mapsto \cl\left(\bigcup_{x \in f(a), y \in g(x)} h_2(y) \times \{y\}\right)\]
    Of course, equality of these maps simply means that the right-hand sides agree for each $x$.

    Let us rewrite and name this set as
    \[S := \cl\left(\{(z,y) \mid z \in h_1(y), y \in \cup_{x \in f(a)} g(x)\}  \right) = \cl\left(\{(z,y) \mid z \in h_2(y), y \in \cup_{x \in f(a)} g(x)\}  \right) \]

    The desired conclusion is that the sets
    \[\cl\left(\bigcup_{x \in f(a), y \in g(x)} h_1(y) \times \{y\} \times \{x\}\right),\ \cl\left(\bigcup_{x \in f(a), y \in g(x)} h_2(y) \times \{y\} \times \{x\}\right)\]
    agree. Let us rewrite them as
    \[\cl\left(\{(z,y,x) \mid z \in h_1(y), y\in g(x), x\in f(a)\}\right),\ \cl\left(\{(z,y,x) \mid z \in h_2(y), y\in g(x), x\in f(a)\}\right)\]

    To show this identity, it suffices to show that 
    \[\{(z,y,x) \mid z \in h_1(y), y\in g(x), x\in f(a)\} \subseteq \cl\left(\{(z,y,x) \mid z \in h_2(y), y\in g(x), x\in f(a)\}\right)\]
    (and the converse inclusion).

    Let us take a point $(z_0,y_0,x_0)$ left-hand set, and consider an open neighborhood $U_1 \times U_2 \times U_3$, for open subsets of $Z,Y,X$ respectively.
    Our goal is to construct $(z,y,x) \in U_1\times U_2 \times U_3$ so that $x \in f(a), y \in g(x), z \in h_2(y)$.

    The assumptions on $(z_0,y_0,x_0)$ implies that the point $(z_0,y_0)$ is in $S$.
    Hence by the other expression of $S$, we can find a point $x$ so that $x \in f(a), y_0 \in g(x) \cap U_2, z_0 \in h_2(y_0) \cap U_1$.
    The issue is now to fix this so that $x \in f(a) \cap U_3$.

    Consider the set $\{y \mid h_2(y) \cap U_1 \neq \emptyset\}$.
    This is an open set which contains our $y_0$ above. Let $U_2'$ be the (nonempty!) intesection of this set with $U_2$.
    Now consider $\{x \mid g(x) \cap U_2' \neq \emptyset\}$. This is again an open set which cantains $x_0$. Let $U_3'$ be the intersection of this with $U_3$.
    Now since $x_0 \in f(a)$, any open neighborhood of $x_0$ intersects $f(a)$ (since it's closed).
    So choose $x_1 \in f(a) \cap U_3', y_1 \in U_2' \cap g(x) \cap U_2',$ and finally $z_1 \in h_2(y) \cap U_1$.
    (Each possible by the construction of the previous element). By construction we have $(z_1,y_1,x_1) \in U_1 \times U_2 \times U_3$, exactly as desired.
    The other inclusion follows by a symmetric argument.
\end{proof}
